### 2012-03-19 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Arithmetic Operations}
If the operator in an arithmetic operation is one of \texttt{+}, \texttt{-}, \texttt{div}, \texttt{mod} (the class of the expression node is \texttt{Operator} and it represents one of \texttt{PLUS}, \texttt{MINUS}, \texttt{IDIV}, \texttt{MOD} (for all operators, see Attachment \ref{FIG_operators})), one operand is of PathType $P$ and the type $T$ of the other operand is one of numeric built-in types, then the inferred statement is $P \rightarrow T$.

If the operator in an arithmetic operation is one of \texttt{*}, \texttt{/} (the class of the expression node is \texttt{Operator} and it represents one of \texttt{MUL}, \texttt{DIV}, one operand is of PathType $P$ and the type $T$ of the other operand is one of numeric built-in types, then the inferred statement is $P \rightarrow $ \texttt{double}.

>>>>

\subsection{Arithmetic Operations}
If the operator in an arithmetic operation is one of \texttt{+}, \texttt{-}, \texttt{div}, \texttt{mod}, \texttt{*}, \texttt{/} (the class of the expression node is \texttt{Operator} and it represents one of \texttt{PLUS}, \texttt{MINUS}, \texttt{IDIV}, \texttt{MOD}, \texttt{MUL}, \texttt{DIV} (for all operators, see Attachment \ref{FIG_operators})), one operand is of PathType $P$ and the type $T$ of the other operand is one of numeric built-in types, then the inferred statement is $P \rightarrow T$.
